\resp{COMPAS Star-formation LnL GP surrogate}

### 2024-06-26 src/tex/ms.tex
[showyourwork] overleaf sync

We build upon Riley at al. (2023)'s work, and

@@

\subsection{MSSFR parameters}\label{sec:method_parameters}

The parameters we chose to vary for this study are four free parameters for the calculation of the \ac{MSSFR} in the phenomenological model of \citet{Neijssel_2019}. In this model, the \ac{MSSFR} is split into two parts, the star formation rate (SFR) and the metallicity distribution:

@@

\subsection{Bayesian Model}
Given $N_{\mathrm{obs}}$ observations from data  $\mathcal{D} \equiv \{D_1, D_2, ... D_{N_{\mathrm{obs}}}\}$, we define the likelihood $\mathcal{L}$ that we will see data $\mathcal{D}$ for a particular set of parameters $\lambda$ as
\begin{equation}
  \log{\Lmain} = \log{\Lp\left(N_{\mathrm{obs}}|\lambda\right)} +
  \sum_{i=1}^{N_\mathrm{obs}} \log{\Le(D_i|\lambda)}\ .
  \label{eq:methods_likelihood}
\end{equation}

@@

We get the data from the \ogc.
Plots of the event $\Mc,z$ median estimates and $X-\sigma$ uncertainty can be found in Figure X in the Appendix.

@@

We do not 
\begin{itemize}
    \item Do hyper-parameter optimisation for the GP (kernal choices, kernel settings) 
    \item Do hyper-parameter optimisation for the acquisition function 
    \item Explore range of acquisition functions
\end{itemize}

@@

\section{OGC4 Events}

\begin{figure}[ht!]
    \script{plot_ogc4_events.py}
    \begin{centering}
        \includegraphics[width=0.8\columnwidth]{figures/ogc4_events.pdf}
        \caption{
            The events and uncertainty as predicted by Ogc4
        }
        \label{fig:ogc4_events}
    \end{centering}
\end{figure}

\section{$\pi(\mathcal{M}, D_{C})$ to $\pi(\mathcal{M}, z)$}

See \cite{Hogg:1999:arXiv} for transforms

\begin{equation}
\Omega_{\rm M}\equiv\frac{8\pi\,G\,\rho_0}{3\,H_0^2}
\end{equation}
\begin{equation}
\Omega_{\Lambda}\equiv\frac{\Lambda\,c^2}{3\,H_0^2}
\end{equation}
\begin{equation}
    D_H = c / H_0
\end{equation}

\begin{equation}
\label{eq:ez}
E(z)\equiv\sqrt{\Omega_{\rm M}\,(1+z)^3+\Omega_k\,(1+z)^2+\Omega_{\Lambda}}
\end{equation}

\begin{equation}
D_{\rm C} = D_{\rm H}\,\int_0^z\frac{dz'}{E(z')}
\end{equation}

The comoving distance between two events at the same redshift or
distance but separated on the sky by some angle $\delta\theta$ is
$D_{\rm M}\,\delta\theta$ and the transverse comoving distance $D_{\rm
M}$ (so-denoted for a reason explained below) is simply related to the
line-of-sight comoving distance $D_{\rm C}$:
\begin{equation}
D_{\rm M} = \left\{
\begin{array}{ll}
D_{\rm H}\,\frac{1}{\sqrt{\Omega_k}}\,\sinh\left[\sqrt{\Omega_k}\,D_{\rm C}/D_{\rm H}\right] & {\rm for}~\Omega_k>0 \\
D_{\rm C} & {\rm for}~\Omega_k=0 \\
D_{\rm H}\,\frac{1}{\sqrt{|\Omega_k|}}\,\sin\left[\sqrt{|\Omega_k|}\,D_{\rm C}/D_{\rm H}\right] & {\rm for}~\Omega_k<0
\end{array}
\right.
\end{equation}

Angular diameter distance is related to the
transverse comoving distance by
\begin{equation}
D_{\rm A} = \frac{D_{\rm M}}{1+z}
\end{equation}

The comoving volume element in solid
angle $d\Omega$ and redshift interval $dz$ is
\begin{equation}
dV_{\rm C}= D_{\rm H}\,\frac{(1+z)^2\,D_{\rm A}^2}{E(z)}\,d\Omega\,dz
\end{equation}

 The integral of the comoving volume element
from the present to redshift $z$ gives the total comoving volume,
all-sky, out to redshift $z$

\begin{equation}
V_{\rm C} = \left\{
\begin{array}{ll}
  \left(\frac{4\pi\,D_{\rm H}^3}{2\,\Omega_k}\right)\,
  \left[\frac{D_{\rm M}}{D_{\rm H}}\,
  \sqrt{1+\Omega_k\,\frac{D_{\rm M}^2}{D_{\rm H}^2}}
  -\frac{1}{\sqrt{|\Omega_k|}}\,
  {\rm arcsinh}\left(\sqrt{|\Omega_k|}\,\frac{D_{\rm M}}{D_{\rm H}}\right)\right]
  & {\rm for}~\Omega_k>0 \\
  \frac{4\pi}{3}\,D_{\rm M}^3
  & {\rm for}~\Omega_k=0 \\
  \left(\frac{4\pi\,D_{\rm H}^3}{2\,\Omega_k}\right)\,
  \left[\frac{D_{\rm M}}{D_{\rm H}}\,
  \sqrt{1+\Omega_k\,\frac{D_{\rm M}^2}{D_{\rm H}^2}}
  -\frac{1}{\sqrt{|\Omega_k|}}\,
  {\rm arcsin}\left(\sqrt{|\Omega_k|}\,\frac{D_{\rm M}}{D_{\rm H}}\right)\right]
  & {\rm for}~\Omega_k<0
\end{array}
\right.
\end{equation}

>>>>

We build upon \citep{Riley:2023:ApJ}'s work, and

@@

\subsection{MSSFR parameters}\label{sec:method_parameters}
\avi{SECTION TAKEN FROM \citep{Riley:2023:ApJ}, FIGURE OUT OUT HOW CONDENSE}
The parameters we chose to vary for this study are four free parameters for the calculation of the \ac{MSSFR} in the phenomenological model of \citet{Neijssel_2019}. In this model, the \ac{MSSFR} is split into two parts, the star formation rate (SFR) and the metallicity distribution:

@@

\subsection{Bayesian Model}
We use the Bayesian model described in \citep{Riley:2023:ApJ}.
Given $N_{\mathrm{obs}}$ observations from data  $\mathcal{D} \equiv \{D_1, D_2, ... D_{N_{\mathrm{obs}}}\}$, we define the likelihood $\mathcal{L}$ that we will see data $\mathcal{D}$ for a particular set of parameters $\lambda$ as
\begin{equation}
  \log{\Lmain} = \log{\Lp\left(N_{\mathrm{obs}}|\lambda\right)} +
  \sum_{i=1}^{N_\mathrm{obs}} \log{\Le(D_i|\lambda)}\ .
  \label{eq:methods_likelihood}
\end{equation}

@@

We get the data from the \ogc.
Plots of the event $\Mc,z$ median estimates and $X-\sigma$ uncertainty can be found in Figure~\ref{fig:ogc4_events} in the Appendix~\ref{}. 
Filtering the events based on the OGC definition of $p(bbh)\geq0.95$ and ensuring that the median value of the $p(\Mc,z|d_i)$ lies within $\Mc\in[4,45]$, $z\in[0,1]$, we get XX events. 
These are colored green in Fig~\ref{fig:ogc4_events}.

Using Equation~\ref{}, we obtain the weights for each posterior. 
A plot of each event's weights summed together is shown in Figure~\ref{fig:ogc4_weights}.

@@

Future work
\begin{itemize}
    \item Do hyper-parameter optimisation for the GP (kernal choices, kernel settings) 
    \item Do hyper-parameter optimisation for the acquisition function 
    \item Explore range of acquisition functions
\end{itemize}

@@

\section{Interfacing with OGC4}

The OGC events are shown in Figure~\ref{fig:ogc4_events}.

\begin{figure}[ht!]
    \script{plot_ogc4_events.py}
    \begin{centering}
        \includegraphics[width=0.35\columnwidth]{figures/ogc4_events.pdf}
        \caption{
            The events and uncertainty as predicted by Ogc4
        }
        \label{fig:ogc4_events}
    \end{centering}
\end{figure}

The priors for the events are in $\pi(\Mc,V_c)$, however, we need $\pi(\Mc,z)$. To transform the priors, we use the following equation
\begin{equation}
    \pi(\Mc,z) = \pi(\Mc, V_c(z)) \frac{d V_c(z)}{dz}\, .
\end{equation}
We use the definition of $d V_c(z)/dz$ from \citep{Hogg:1999:arXiv}, given by 
\begin{equation}
dV_{\rm C}= D_{\rm H}\,\frac{(1+z)^2\,D_{\rm A}^2}{E(z)}\,d\Omega\,dz
\end{equation}
